Raman sideband cooling of single sodium atom to 3D ground state

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] no before axial plot

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba_nol.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}

>>>>

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}
